Realizing temporal graphs from fastest travel times

### 2023-09-22 STACS2023/nina_shortversion.tex

To overcome the above mentioned difficulties, we propose the following high-level strategy.
\begin{itemize}
    \item We identify a small number of ``interesting vertices'' and specific ``graph constructions'' between which we guess representative fastest paths.
    \item For each guess %(also called ``paths configuration'') 
    we create one Integer Linear Program (ILP).
    \item We show that we can determine most labels along each path up to an additive constant. We show that the number of labels we cannot determine is small. 
    \item For each additive constant and each non-determined label we introduce a variable for an Integer Linear Program (ILP).
    \item We use equality and inequality constraints in each ILP to ensure that the fastest temporal path from $u$ to $v$ is of duration $D_{u,v}$, while any other path is of duration at least $D_{u,v}$.
    \item We compute a solution to each of the ILPs (if it exists) and construct a labeling from that solution. Since each ILP has a few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
    If none of the ILP instances give a positive solution, then there exists no labeling realizing given matrix.
    This is true because considering all guesses of fastest temporal paths is equivalent to exhaustively searching through all possible temporal paths between vertices.
\end{itemize}

>>>>

To overcome the above mentioned difficulties, we propose the following high-level strategy.
\begin{itemize}
    \item We identify a small number of ``interesting vertices'' and specific ``graph constructions'' between which we guess representative fastest paths.
    \item For each guess %(also called ``paths configuration'') 
    we create one Integer Linear Program (ILP).
    \item We show that we can determine most labels along each path. We show that the number of labels we cannot determine is small. 
    \item For each non-determined label we introduce a variable for an ILP.
    \item We use equality and inequality constraints in each ILP to ensure that the fastest temporal path from $u$ to $v$ is of duration $D_{u,v}$, while any other path is of duration at least $D_{u,v}$.
    \item We compute a solution to each of the ILPs (if it exists) and construct a labeling from that solution. Since each ILP has a few variables and not too many constraints, this computation can be done efficiently using Lenstra's Theorem~\cite{Lenstra1983Integer}.
    If none of the ILP instances give a positive solution, then there exists no labeling realizing given matrix.
    This is true because considering all guesses of fastest temporal paths is equivalent to exhaustively searching through all possible temporal paths between vertices.
\end{itemize}
